### 2018-06-05 Sections/optimising_the_world.tex
Minor

In the context of a search tree\index{Search tree}, the size of the search space\index{Search space} is,
\begin{align}
s=b^d,
\end{align}
where $b$ is the tree's branching parameter (assumed uniform here for simplicity) and $d$ is tree depth. A quadratic enhancement in the searchable search space to,
\begin{align}
s'=s^2,
\end{align}
effectively doubles the search tree depth that can be accommodated by a given number of oracle calls to,
\begin{align}
d'=2d.
\end{align}

>>>>

In the context of a search tree\index{Search tree}, the size of the search space\index{Search space} (i.e number of leaves on the tree) is \mbox{$s=b^d$},
where $b$ is the tree's branching parameter (assumed uniform here for simplicity) and $d$ is tree depth. A quadratic enhancement in the searchable search space to \mbox{$s'=s^2$} effectively doubles the search tree depth that can be accommodated by a given number of oracle calls to \mbox{$d'=2d$}.
